Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-26 RR_manuscript/Draft_RR.tex
:memo: - render RR with plots and bib

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (Camerer et al., 2018; e.g., Open Science Collaboration, 2015) leading to what is now referred to as the \emph{replication crisis}.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (``I knew it,'' Nickerson 1998), and perceiving events as being plausible in hindsight (``I knew it all along,'' Fischhoff 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g.~Simmons et al.~2011, Gelman \& Loken 2013).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).

While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.

@@

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g.~Ladd 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2009; White, Payne, \& Mattys, 2009).

@@

(2a) ``I can't bear ANOTHER meeting on zoom.''
(2b) ``I can't bear another meeting on ZOOM.''

@@

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/stefano/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words ``another is highlighted by the green box'\,'; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
\end{figure}

Do we only compare the word \emph{another} in 2a and 2b or also the word \emph{zoom} or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
Do we average the domain or do we measure a specific point in time? Do we measure fundamental frequency or intensity? When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes. This plurality of analytical paths is illustrated in figure X. When comparing two utterance such as 2a and 2b, there are many things to consider. Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified. Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint. We could also measure the value or time of the minimum or maximum f0 value. We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0. And the garden of forking paths does not stop here. In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS. Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.).
Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017) in R (R Core Team, 2020).
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

The outcome variable will be the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight 2000).
The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{team}[i]}\) (\(HalfCauchy(0, 1)\)).
We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017).
The code used to run the model can be found here: INSERT LINK.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-burkner2017}{}%
Bürkner, P.-C. (2017). Brms: An {R} package for {B}ayesian multilevel models using {S}tan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28.

@@

@@

@@

\leavevmode\hypertarget{ref-ogden2009}{}%
Ogden, R. (2009). \emph{An introduction to {E}nglish phonetics}. Edinburgh University Press.

@@

\leavevmode\hypertarget{ref-r-core-team2020}{}%
R Core Team. (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.

\leavevmode\hypertarget{ref-stan-development-team2020a}{}%
Stan Development Team. (2020a). RStan: The r interface to stan. R package version 2.21.2.

\leavevmode\hypertarget{ref-stan-development-team2020}{}%
Stan Development Team. (2020b). Stan modeling language users guide and reference manual, 2.25.

@@

@@

>>>>

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (Camerer et al., 2018; e.g., Open Science Collaboration, 2015) leading to what is now referred to as the \emph{replication crisis}.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, \& Dubé, 2015; Starns et al., 2019) and is, among other things, rooted in the inherent flexibility of data analysis (Gelman \& Loken, 2014; often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011).
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box, 1976; De Groot, 2014; Tukey, 1977).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, \& Simonsohn, 2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (Botvinik-Nezer et al., 2020; e.g., Silberzahn et al., 2018; Starns et al., 2019).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (Gelman \& Loken, 2014; e.g., Simmons, Nelson, \& Simonsohn, 2011).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).

While this issue has been widely discussed both from a conceptual point of view (Nosek \& Lakens, 2014; Simmons, Nelson, \& Simonsohn, 2011; Wagenmakers, Wetzels, Borsboom, Maas, \& Kievit, 2012) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger, 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.

@@

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories {[}e.g., Jongman, Wayland, and Wong (2000); Lisker (1986); Summerfield, 1984; Winter (2014){]}.
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon \& Roettger, 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).

@@

(2a) ``I can't bear ANOTHER meeting on zoom.''\\
(2b) ``I can't bear another meeting on ZOOM.''

@@

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words ``another is highlighted by the green box'\,'; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
\end{figure}

Do we only compare the word \emph{another} in 2a and 2b or also the word \emph{zoom} or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
Do we average the domain or do we measure a specific point in time?
Do we measure fundamental frequency or intensity?
When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
This plurality of analytical paths is illustrated in figure X.
When comparing two utterance such as 2a and 2b, there are many things to consider.
Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
And the garden of forking paths does not stop here.
In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.~????).
Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}) in R (\textbf{r-core-team2020?}).
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

The outcome variable will be the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight, 2000).
The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{team}[i]}\) (\(HalfCauchy(0, 1)\)).
We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
The analysis will be conducted in R (\textbf{r-core-team2020?}) and fit using Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}).
The code used to run the model can be found here: INSERT LINK.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-arts2011overspecification}{}%
Arts, A., Maes, A., Noordman, L. G., \& Jansen, C. (2011). Overspecification in written instruction. \emph{Linguistics}, \emph{49}(3), 555--574.

\leavevmode\hypertarget{ref-botvinik2020variability}{}%
Botvinik-Nezer, R., Holzmeister, F., Camerer, C. F., Dreber, A., Huber, J., Johannesson, M., \ldots{} others. (2020). Variability in the analysis of a single neuroimaging dataset by many teams. \emph{Nature}, 1--7.

\leavevmode\hypertarget{ref-box1976science}{}%
Box, G. E. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799.

@@

\leavevmode\hypertarget{ref-de2014thought}{}%
De Groot, A. D. (2014). \emph{Thought and choice in chess} (Vol. 4). Walter de Gruyter GmbH \& Co KG.

\leavevmode\hypertarget{ref-degen2020redundancy}{}%
Degen, J., Hawkins, R. D., Graf, C., Kreiss, E., \& Goodman, N. D. (2020). When redundancy is useful: A bayesian approach to {``overinformative''} referring expressions. \emph{Psychological Review}.

@@

\leavevmode\hypertarget{ref-gatt2013we}{}%
Gatt, A., Gompel, R. P. van, Deemter, K. van, \& Krahmer, E. (2013). Are we bayesian referring expression generators. Cognitive Science Society.

\leavevmode\hypertarget{ref-gelman2014statistical}{}%
Gelman, A., \& Loken, E. (2014). The statistical crisis in science: Data-dependent analysis--a" garden of forking paths"--explains why many statistically significant comparisons don't hold up. \emph{American Scientist}, \emph{102}(6), 460--466.

\leavevmode\hypertarget{ref-gordon2017acoustic}{}%
Gordon, M., \& Roettger, T. (2017). Acoustic correlates of word stress: A cross-linguistic survey. \emph{Linguistics Vanguard}, \emph{3}(1), 1--11.

\leavevmode\hypertarget{ref-grice1975logic}{}%
Grice, H. P. (1975). Logic and conversation. In \emph{Speech acts} (pp. 41--58). Brill.

\leavevmode\hypertarget{ref-hawkins2004influence}{}%
Hawkins, S., \& Nguyen, N. (2004). Influence of syllable-coda voicing on the acoustic properties of syllable-onset /l/ in {E}nglish. \emph{Journal of Phonetics}, \emph{32}(2), 199--231.

\leavevmode\hypertarget{ref-jongman2000acoustic}{}%
Jongman, A., Wayland, R., \& Wong, S. (2000). Acoustic characteristics of english fricatives. \emph{The Journal of the Acoustical Society of America}, \emph{108}(3), 1252--1263.

\leavevmode\hypertarget{ref-knight2000}{}%
Knight, K. (2000). \emph{Mathematical statistics}. Chapman; Hall, New York.

\leavevmode\hypertarget{ref-koole2012rewarding}{}%
Koole, S. L., \& Lakens, D. (2012). Rewarding replications: A sure and simple way to improve psychological science. \emph{Perspectives on Psychological Science}, \emph{7}(6), 608--614.

\leavevmode\hypertarget{ref-ladd2008intonational}{}%
Ladd, D. R. (2008). \emph{Intonational phonology}. Cambridge University Press.

@@

\leavevmode\hypertarget{ref-lisker1977rapid}{}%
Lisker, L. (1977). Rapid versus rabid: A catalogue of acoustic features that may cue the distinction. \emph{The Journal of the Acoustical Society of America}, \emph{62}(S1), S77--S78.

\leavevmode\hypertarget{ref-lisker1986voicing}{}%
Lisker, L. (1986). {``Voicing''} in {E}nglish: A catalogue of acoustic features signaling /b/ versus /p/ in trochees. \emph{Language and Speech}, \emph{29}(1), 3--11.

\leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
Nickerson, R. S. (1998). Confirmation bias: A ubiquitous phenomenon in many guises. \emph{Review of General Psychology}, \emph{2}(2), 175--220.

\leavevmode\hypertarget{ref-nosek2014method}{}%
Nosek, B. A., \& Lakens, D. (2014). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137--141.

\leavevmode\hypertarget{ref-ogden2004}{}%
Ogden, R. (2004). Non-modal voice quality and turn-taking in {F}innish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.

@@

\leavevmode\hypertarget{ref-paraboni2007generating}{}%
Paraboni, I., Van Deemter, K., \& Masthoff, J. (2007). Generating referring expressions: Making referents easy to identify. \emph{Computational Linguistics}, \emph{33}(2), 229--254.

\leavevmode\hypertarget{ref-roettger2019researcher}{}%
Roettger, T. B. (2019). Researcher degrees of freedom in phonetic research. \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology}, \emph{10}(1).

\leavevmode\hypertarget{ref-rotello2015more}{}%
Rotello, C. M., Heit, E., \& Dubé, C. (2015). When more data steer us wrong: {R}eplications with the wrong dependent measure perpetuate erroneous conclusions. \emph{Psychonomic Bulletin \& Review}, \emph{22}(4), 944--954.

\leavevmode\hypertarget{ref-rubio2016redundant}{}%
Rubio-Fernández, P. (2016). How redundant are redundant color adjectives? An efficiency-based analysis of color overspecification. \emph{Frontiers in Psychology}, \emph{7}, 153.

\leavevmode\hypertarget{ref-sedivy2003pragmatic}{}%
Sedivy, J. C. (2003). Pragmatic versus form-based accounts of referential contrast: Evidence for effects of informativity expectations. \emph{Journal of Psycholinguistic Research}, \emph{32}(1), 3--23.

\leavevmode\hypertarget{ref-silberzahn2018many}{}%
Silberzahn, R., Uhlmann, E. L., Martin, D. P., Anselmi, P., Aust, F., Awtrey, E., \ldots{} others. (2018). Many analysts, one data set: Making transparent how variations in analytic choices affect results. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337--356.

\leavevmode\hypertarget{ref-simmons2011false}{}%
Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2011). False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant. \emph{Psychological Science}, \emph{22}(11), 1359--1366.

\leavevmode\hypertarget{ref-starns2019assessing}{}%
Starns, J. J., Cataldo, A. M., Rotello, C. M., Annis, J., Aschenbrenner, A., Bröder, A., \ldots{} Wilson, J. (2019). Assessing theoretical conclusions with blinded inference to investigate a potential inference crisis. \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 335--349.

\leavevmode\hypertarget{ref-sterling1959publication}{}%
Sterling, T. D. (1959). Publication decisions and their possible effects on inferences drawn from tests of significance---or vice versa. \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.

@@

\leavevmode\hypertarget{ref-tukey1977exploratory}{}%
Tukey, J. W. (1977). \emph{Exploratory data analysis} (Vol. 2). Reading, MA.

\leavevmode\hypertarget{ref-tversky1974judgment}{}%
Tversky, A., \& Kahneman, D. (1974). Judgment under uncertainty: Heuristics and biases. \emph{Science}, \emph{185}(4157), 1124--1131.

\leavevmode\hypertarget{ref-van2005speech}{}%
Van Heuven, V. J., \& Van Zanten, E. (2005). Speech rate as a secondary prosodic characteristic of polarity questions in three languages. \emph{Speech Communication}, \emph{47}(1-2), 87--99.

\leavevmode\hypertarget{ref-wagenmakers2012agenda}{}%
Wagenmakers, E.-J., Wetzels, R., Borsboom, D., Maas, H. L. van der, \& Kievit, R. A. (2012). An agenda for purely confirmatory research. \emph{Perspectives on Psychological Science}, \emph{7}(6), 632--638.

\leavevmode\hypertarget{ref-westerbeek2015stored}{}%
Westerbeek, H., Koolen, R., \& Maes, A. (2015). Stored object knowledge and the production of referring expressions: The case of color typicality. \emph{Frontiers in Psychology}, \emph{6}, 935.

@@

\leavevmode\hypertarget{ref-wicherts2006poor}{}%
Wicherts, J. M., Borsboom, D., Kats, J., \& Molenaar, D. (2006). The poor availability of psychological research data for reanalysis. \emph{American Psychologist}, \emph{61}(7), 726.

\leavevmode\hypertarget{ref-winter2014spoken}{}%
Winter, B. (2014). Spoken language achieves robustness and evolvability by exploiting degeneracy and neutrality. \emph{BioEssays}, \emph{36}(10), 960--967.
